---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# travis badge
![Build Status](https://api.travis-ci.org/alex2905/coursera.svg?branch=master)


# coursera

This package and the functions in it, use data from US National Highway Traffic 
Safety Administration's Fatality Analysis Reporting System. The purpose is to 
illustrate the correctness of the documentation and creation of a package.
The purpose of the functions itself, is to show the accidents per state per 
country for each year, where each year corresponds to a separate dataset.
For more details see the vignette of the package.

## Installation

You can install coursera from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("alex2905/coursera")
```

## Example plot for state 1 in year 2013

```{r example, echo = FALSE}
library(coursera)
fars_map_state(1,2013)
```
