---
title: "Testing the correctness of the creation of a package"
author: "Alexander Kurtz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Testing the correctness of the creation of a package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package and the functions in it, use data from US National Highway Traffic 
Safety Administration's Fatality Analysis Reporting System. The purpose is to 
illustrate the correctness of the documentation and creation of a package.
The purpose of the functions itself,is to show the accidents per state per 
country for each year, where each year corresponds to a separate dataset.

# Function Info

## Generic functions

There are two generic functions: \n
`fars_read` and `make_filename` which are just built for this special case to
load the zipped bz2 file to R and create the approriate name of the zipped file.

## fars_read_years

## fars_summarize_years

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
