---
title: "Testing the correctness of the creation of a package"
author: "Alexander Kurtz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Testing the correctness of the creation of a package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package and the functions in it, use data from US National Highway Traffic 
Safety Administration's Fatality Analysis Reporting System. The purpose is to 
illustrate the correctness of the documentation and creation of a package.
The purpose of the functions itself, is to show the accidents per state per 
country for each year, where each year corresponds to a separate dataset.

## Function Info

### Generic functions

There are two generic functions:  
`fars_read` and `make_filename`, which are just built for this special case to
load the zipped bz2 file to R and create the approriate name of the zipped file.

### `fars_read_years` and `fars_summarize_years`
`fars_read_years` creates a dataset, containing the month and year information 
for each observation. The `fars_summarize_years` function takes the previous data 
as a starting point and calculates the overview of the number of accidents per 
month per year. The year corresponds to the dataset.


### `fars_map_state`
Plot the overview of the locations of each accident in one state in one year.

###### Example plot for state 1 in year 2013

```{r, fig.show='hold', echo = FALSE}
library(coursera)
setwd("..")
fars_map_state(1,2013)
setwd("vignettes")
```

### Details
For more details of each function check their documentation.
